---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FEprovideR
## Fixed effects logistic model with high-dimensional parameters
<!-- badges: start -->
<!-- badges: end -->

A stuctured profile likelihood algorithm for the logistic fixed effects model and an aproximate EM algorithm for the logistic mixed effects model. 

## Installation

You can install the released version of FEprovideR from [Github](https://github.com/umich-biostatistics/FEprovideR) with:

``` r
install.packages("devtools") # you need devtools to install packages from Github
devtools::install_github("umich-biostatistics/FEprovideR")
```

## Example

This tutorial simulates a data set to demonstrate the functions provided by FRprovideR.

```{r example, eval=FALSE}
# load the package
library(FEprovideR)

# other imports
library(Matrix)
library(poibin)
library(ggplot2)
```

To simulate a data set, use the following code chunk:

```{r example.simuate.data, eval=FALSE}
# Simulate a data set
m <- 500
prov.size <- pmax(round(rnorm(m, 50, 15)),11)
gamma <- rnorm(m, log(3/7), 0.4)
beta <- c(1,0.5,-1)
Y.char <- 'Y'
prov.char <- 'prov.ID'
Z.char <- paste0('z', 1:length(beta))
data <- sim.fe.prov(m, prov.size, gamma, beta, Y.char, Z.char, prov.char)
```

This data is also available in the included data sets that come with the package.
To use the included data, run:

```{r, eval=FALSE}
data(hospital)            # raw data
data(hospital_prepared)   # processed data
```


Now, set relevant parameters and fit a model to the prepared data:

```{r example.fit, eval=FALSE}
# a small positive number specifying stopping criterion of Newton-Raphson algorithm
tol <- 1e-5  
# Name input variables and other parameters
Y.char <- 'Y'
prov.char <- 'prov.ID'
Z.char <- paste0('z', 1:3)
data(hospital_prepared) # build in data set
fe.ls <- fe.prov(hospital_prepared, Y.char, Z.char, prov.char, tol) # model fitting
```

Conduct hypothesis tests on the estimated standardized readmission ratios (SSRs):

```{r example.hypothesis.testing, eval=FALSE}
# hypothesis testing
null <- "median"
n <- 10000
score.fe <- test.fe.prov(hospital_prepared, fe.ls, Y.char, Z.char, prov.char, test="score", null, alpha)
exact.pb <- test.fe.prov(hospital_prepared, fe.ls, Y.char, Z.char, prov.char, test="exact.poisbinom", null, alpha)
exact.bs <- test.fe.prov(hospital_prepared, fe.ls, Y.char, Z.char, prov.char, test="exact.bootstrap", null, alpha, n)
exact.binom <- test.fe.prov(hospital_prepared, fe.ls, Y.char, Z.char, prov.char, test="exact.binom", null="median", alpha)
```

Compute confidence intervals for the estimated SSRs:

```{r example.confindence.intervals, eval=FALSE}
# confidence intervals
confint.df <- confint.fe.prov(fe.ls, parm = "all", level = 0.95, hospital_prepared, Y.char, Z.char, prov.char)
confint.df <- confint.fe.prov(fe.ls, parm = "all", level = 0.90, hospital_prepared, Y.char, Z.char, prov.char)
confint.df <- confint.fe.prov(fe.ls, level = 0.90, data = hospital_prepared, Y.char = Y.char, Z.char = Z.char, prov.char = prov.char)
```

## Funnel plots for SRRs (Standardized readmission ratios)

```{r funnel.plot.prep, eval=FALSE}
# format input data for funnel plot
input.dis <- data.frame(ID=hospital_prepared[hospital_prepared$included==1, prov.char],
                        prob=fe.ls$Exp)
input.prov <- data.frame(SRR=fe.ls$df.prov$SRR, flag=score.fe$flag)
```

Score test based funnel plot:

```{r funnel.score.test, eval=FALSE}
input.prov <- data.frame(SRR=fe.ls$df.prov$SRR, flag=score.fe$flag)
funnel.SRR(input.dis, input.prov, target, alphas, type="FE.score")
```


